Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-16 1047_supp.tex
add
a

\section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
For notation simplicity, we ignore the indices $n,m,t$ in problem (6) of the main paper. And it turns into the following weighted sparse coding problem:
\vspace{-4mm}
\begin{equation}\label{equ1}\vspace{-2mm}
\min_{\bm{\alpha}}\|\mathbf{y}-\mathbf{D}\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
\end{equation}
Since $\mathbf{D}$ is an orthogonal matrix, problem (\ref{equ1}) is equivalent to 
\vspace{-2mm}
\begin{equation}\label{equ2}\vspace{-2mm}
\min_{\bm{\alpha}}\|\mathbf{D}^{T}\mathbf{y}-\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
\end{equation}
For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as
\vspace{-2mm}
\begin{equation}\label{equ3}\vspace{-2mm}
\min_{\boldsymbol{\alpha}}\sum_{j=1}^{3p^2}((\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|).
\end{equation}
The problem (\ref{equ3}) is separable w.r.t. each $\bm{\alpha}_{j}$ and hence can be simplified to $3p^2$ independent  scalar minimization problems
\vspace{-2mm}
\begin{equation}\label{equ4}\vspace{-2mm}
\min_{\bm{\alpha}_{j}}(\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|,
\end{equation}
where $j=1,...,3p^2$. Taking derivative of $\boldsymbol{\alpha}_{j}$ in problem (\ref{equ4}) and setting the derivative to be zero. There are two cases for the solution.

@@

\section{More Results on Real Noisy Images in \cite{ncwebsite}}
In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods. One can seen from Figures \ref{fig1}-\ref{fig4} that, our proposed method perfomrs better than the state-of-the-art denoising methods.

>>>>

\section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
For notation simplicity, we ignore the indices $n,m,t$ in problem (6) of the main paper. It turns into the following weighted sparse coding problem:
\vspace{-4mm}
\begin{equation}\label{equ1}\vspace{-2mm}
\min_{\bm{\alpha}}\|\mathbf{y}-\mathbf{D}\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
\end{equation}
Since $\mathbf{D}$ is an orthogonal matrix, problem (\ref{equ1}) is equivalent to 
\vspace{-2mm}
\begin{equation}\label{equ2}\vspace{-2mm}
\min_{\bm{\alpha}}\|\mathbf{D}^{T}\mathbf{y}-\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
\end{equation}
For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as
\vspace{-2mm}
\begin{equation}\label{equ3}\vspace{-2mm}
\min_{\boldsymbol{\alpha}}\sum_{j=1}^{3p^2}((\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|).
\end{equation}
The problem (\ref{equ3}) is separable w.r.t. each $\bm{\alpha}_{j}$ and hence can be simplified to $3p^2$ independent  scalar minimization problems
\vspace{-2mm}
\begin{equation}\label{equ4}\vspace{-2mm}
\min_{\bm{\alpha}_{j}}(\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|,
\end{equation}
where $j=1,...,3p^2$. Taking derivative of $\boldsymbol{\alpha}_{j}$ in problem (\ref{equ4}) and setting the derivative to be zero. There are two cases for the solution.

@@

\section{More Results on Real Noisy Images in \cite{ncwebsite}}
In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods. As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the state-of-the-art denoising methods.
